Using best practices for forecasting biodiversity changes in breeding birds

### 2017-07-20 manuscript/draft.Rmd

@@

**Time series models.** We used Auto-ARIMA models [based on the `auto.arima`
function in @forecast1] to represent a array of different time-series modeling
approaches. These models can include an autoregressive component (as in the
"naive" model, but with the possibility of longer-term dependencies in the
underlying process), a moving average component (where the noise can have serial
autocorrelation) and an integration/differencing component (so that the analysis
could be performed on sequential differences of the raw data, accommodating more
complex patterns including trends). The `auto.arima` function chooses whether to
include each of these components, and how many terms to include for each one,
using AICc [@forecast1]. Since there is no seasonal component to the BBS
time-series, we did not include a season component in these models. Otherwise we
used the default settings for this function. [[Note: should probably record
somewhere what order model the auto.arima function tends to choose.  Eyeballing
the results, seems to be most similar to the naive model, but would be good to
check.]]

@@

While the models generally did well in absolute terms (Figure 2), they tended
not to outperform the "average" baseline from the generalized linear mixed model
(Figure 3A). [[Stats go here]].  The auto-ARIMA was generally the best-performing
non-baseline model, but in many cases, the best-fitting ARIMA model chosen by
the model selection procedure was no different from the "average" model.

>>>>

## Abstract

@@

**Time series models.** We used Auto-ARIMA models [based on the `auto.arima`
function in @forecast1] to represent a array of different time-series modeling
approaches. These models can include an autoregressive component (as in the
"naive" model, but with the possibility of longer-term dependencies in the
underlying process), a moving average component (where the noise can have serial
autocorrelation) and an integration/differencing component (so that the analysis
could be performed on sequential differences of the raw data, accommodating more
complex patterns including trends). The `auto.arima` function chooses whether to
include each of these components, and how many terms to include for each one,
using AICc [@forecast1]. Since there is no seasonal component to the BBS
time-series, we did not include a season component in these models. Otherwise we
used the default settings for this function.

@@

While the models generally did well in absolute terms (Figure 2), they tended
not to outperform the "average" baseline from the generalized linear mixed model
(Figure 3A). [[Stats go here]].  The auto-ARIMA was generally the
best-performing non-baseline model, but in many cases (67% of the time), the
best-fitting ARIMA model chosen by the model selection procedure had no
autoregressive, drift, or moving average terms, making it similar to the
"Average" model.
